Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-15 analysis/paper/paper.Rmd
add supplementary materials section

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

>>>>

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
```

# Supplementary Materials

## Tables

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
parameters(m_f1) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  as_tibble() %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit()
```

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
parameters(m_f2) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  as_tibble() %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit()
```

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
parameters(m_h1) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  as_tibble() %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit()
```

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
parameters(m_h2) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  as_tibble() %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit()
```
